### 2024-12-02 paper/paper.qmd
change the title of graphs

---
title: ""
subtitle: ""
author: 
  - Yawen Tan
thanks: "Code and data are available at: [https://github.com/YawennnnnnTan/Analysis-of-Diamond-Price]"
date: today
date-format: long
abstract: ""
format: pdf
number-sections: true
bibliography: 
  - references.bib
toc: true
---

@@

library(readr)
library(arrow)
library(here)
library(ggplot2)
library(patchwork)
library(ggplot2)

@@

### Color

@@

color_histogram_plot <- ggplot(cleaned_data, aes(x = color)) +
  geom_bar(binwidth = 3,fill = "pink", color = "black", alpha = 0.7) + 
  #scale_x_continuous(
  #  breaks = 1:8, 
  #  labels = c("D", "E", "F", "G", "H", "I", "J", "K"))+
  labs(
    title ="Distribution of Variable: Color",
    x = "Diamond Color",
    y = "Count") +
  theme_minimal() # Use a minimal theme for clean visualization

# 绘制小提琴图
violin_plot_color <- ggplot(cleaned_data, aes(x = color, y = price)) +
  geom_violin(trim = FALSE, fill = "lightblue", alpha = 0.7) +  # 添加小提琴图
  geom_boxplot(width = 0.2, outlier.color = "salmon", outlier.shape = 8, alpha = 0.7) +  # 在小提琴图中叠加箱线图
  labs(
    title = "Violin Plot of Price by Color",
    x = "Diamond Color",
    y = "Diamond Price (USD)"
  ) +
  theme_minimal()  # 使用简洁的主题

@@

# Graph histogram
# Calculate the mean of diamond prices
mean_size <- mean(cleaned_data$carat_size, na.rm = TRUE)
carat_size_histogram_plot <- ggplot(cleaned_data, aes(x = carat_size)) +
  geom_histogram(fill = "palevioletred", color = "black", alpha = 0.7) +
  geom_vline(xintercept = mean_size, linetype = "dashed", color = "salmon") +
  labs(
    title = "Distribution of Variable: Carat Size",
    x = "Diamond Carat Size",
    y = "Count"
  ) +
  theme_minimal() # Use a minimal theme for clean visualization

plot_carat_size <- ggplot(cleaned_data, aes(x = carat_size, y = price)) +
  geom_point(color = "lightblue", alpha = 0.7) +
  geom_smooth(method = "loess", color = "black", se = FALSE) +
  labs(
    title = "Carat Size vs Price",
    x = "Carat Size",
    y = "Diamond Price (USD)"
  ) +
  theme_minimal()

@@

# Graph histogram
# Create the histogram with mean line
clarity_histogram_plot <- ggplot(cleaned_data, aes(x = clarity)) +
  geom_bar(bins = 20, fill = "pink", color = "black", alpha = 0.7) +
  labs(
    title = "Distribution of Variable: Clarity",
    x = "Diamond Clarity",
    y = "Count"
  ) +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

violin_plot_clarity <- ggplot(cleaned_data, aes(x = clarity, y = price)) +
  geom_violin(trim = FALSE, fill = "lightblue", alpha = 0.7) + 
  geom_boxplot(width = 0.2, outlier.color = "salmon", outlier.shape = 8, alpha = 0.7) +
  labs(
    title = "Violin Plot of Price by Clarity",
    x = "Clarity",
    y = "Diamond Price(USD)"
  ) +
  theme_minimal()

@@

# Graph histogram
# Create the histogram with mean line
cut_histogram_plot <- ggplot(cleaned_data, aes(x = cut)) +
  geom_bar(bins = 20, fill = "palevioletred", color = "black", alpha = 0.7)+
  labs(
    title = "Distribution of Variable: Cut",
    x = "Diamond Cut",
    y = "Count"
  ) +
  theme_minimal() # Use a minimal theme for clean visualization

violin_plot_cut <- ggplot(cleaned_data, aes(x = cut, y = price)) +
  geom_violin(trim = FALSE, fill = "lightblue", alpha = 0.7) + 
  geom_boxplot(width = 0.2, outlier.color = "salmon", outlier.shape = 8, alpha = 0.7) +
  labs(
    title = "Violin Plot of Price by Cut",
    x = "Diamond Cut",
    y = "Diamond Price (USD)"
  ) +
  theme_minimal()

@@

# 加载必要的库
library(ggcorrplot)
library(dplyr)

@@

# 检查列名
colnames(one_hot_encoded)

# 检查独热编码后的列名
colnames(one_hot_encoded)

@@

# 检查 color 的实际水平
table(correlated_data$color)

# 检查 clarity 的实际水平
table(correlated_data$clarity)

# 检查 cut 的实际水平
table(correlated_data$cut)

@@

\begin{align} 
- \( x_{1i} \): The carat size of the diamond (in carats).
- \( x_{2i} \): The color grade of the diamond (categorical).
- \( x_{3i} \): The cut grade of the diamond (categorical).
- \( x_{4i} \): The clarity grade of the diamond (categorical).

**Model Structure**:
1. **Response Distribution**:  
   \( y_i \mid \mu_i, \phi \sim \text{Gamma}(\mu_i, \phi) \),  
   where \( \mu_i \) is the mean price and \( \phi \) is the dispersion parameter.

2. **Link Function**:  
   \( \log(\mu_i) = \beta_0 + \beta_1 x_{1i} + \sum_{j} \beta_{2j} \cdot \text{color}_{ij} + \sum_{k} \beta_{3k} \cdot \text{cut}_{ik} + \sum_{l} \beta_{4l} \cdot \text{clarity}_{il} \).

   - \( \beta_0 \): Intercept term.  
   - \( \beta_1 \): Effect of carat size.  
   - \( \beta_{2j}, \beta_{3k}, \beta_{4l} \): Effects of color, cut, and clarity, respectively.

3. **Mean Price**:  
   \( \mu_i = \exp(\beta_0 + \beta_1 x_{1i} + \sum_{j} \beta_{2j} \cdot \text{color}_{ij} + \sum_{k} \beta_{3k} \cdot \text{cut}_{ik} + \sum_{l} \beta_{4l} \cdot \text{clarity}_{il}) \).

\end{align}

>>>>

---
title: ""
subtitle: ""
author: 
  - Yawen Tan
thanks: "Code and data are available at: [https://github.com/YawennnnnnTan/Analysis-of-Diamond-Price]"
date: today
date-format: long
abstract: ""
format: pdf
number-sections: true
bibliography: 
  - references .bib
toc: true
---

@@

library(readr)
library(arrow)
library(here)
library(ggplot2)
library(patchwork)
library(ggplot2)
library(ggcorrplot)
library(dplyr)

@@

### Color
def:
distribution:
vs price:

@@

color_histogram_plot <- ggplot(cleaned_data, aes(x = color)) +
  geom_bar(fill = "pink", color = "black", alpha = 0.7) + 
  labs(
    title ="Distribution of Variable: Color",
    x = "Diamond Color",
    y = "Count") +
  theme_minimal() +
  theme(plot.title = element_text(size = 12, face = "bold",hjust = 0.5 ))

# 绘制小提琴图
violin_plot_color <- ggplot(cleaned_data, aes(x = color, y = price)) +
  geom_violin(trim = FALSE, fill = "lightblue", alpha = 0.7) +  # 添加小提琴图
  geom_boxplot(width = 0.2, outlier.color = "salmon", outlier.shape = 8, alpha = 0.7) +  # 在小提琴图中叠加箱线图
  labs(
    title = "Violin Plot of Price by Color",
    x = "Diamond Color",
    y = "Diamond Price (USD)"
  ) +
  theme_minimal()+
  theme(plot.title = element_text(size = 12, face = "bold",hjust = 0.5 ))

@@

# Graph histogram
# Calculate the mean of diamond prices
mean_size <- mean(cleaned_data$carat_size, na.rm = TRUE)
carat_size_histogram_plot <- ggplot(cleaned_data, aes(x = carat_size)) +
  geom_histogram(fill = "palevioletred", color = "black", alpha = 0.7) +
  geom_vline(xintercept = mean_size, linetype = "dashed", color = "salmon") +
  labs(
    title = "Distribution of Variable: Carat Size",
    x = "Diamond Carat Size",
    y = "Count"
  ) +
  theme_minimal()+
  theme(plot.title = element_text(size = 12, face = "bold",hjust = 0.5 ))

plot_carat_size <- ggplot(cleaned_data, aes(x = carat_size, y = price)) +
  geom_point(color = "lightblue", alpha = 0.7) +
  geom_smooth(method = "loess", color = "black", se = FALSE) +
  labs(
    title = "Carat Size vs Price",
    x = "Carat Size",
    y = "Diamond Price (USD)"
  ) +
  theme_minimal()+
  theme(plot.title = element_text(size = 12, face = "bold",hjust = 0.5))

@@

# Graph histogram
# Create the histogram with mean line
clarity_histogram_plot <- ggplot(cleaned_data, aes(x = clarity)) +
  geom_bar(bins = 20, fill = "pink", color = "black", alpha = 0.7) +
  labs(
    title = "Distribution of Variable: Clarity",
    x = "Diamond Clarity",
    y = "Count"
  ) +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  theme(plot.title = element_text(size = 12, face = "bold",hjust = 0.5))

violin_plot_clarity <- ggplot(cleaned_data, aes(x = clarity, y = price)) +
  geom_violin(trim = FALSE, fill = "lightblue", alpha = 0.7) + 
  geom_boxplot(width = 0.2, outlier.color = "salmon", outlier.shape = 8, alpha = 0.7) +
  labs(
    title = "Violin Plot of Price by Clarity",
    x = "Clarity",
    y = "Diamond Price(USD)"
  ) +
  theme_minimal()+
  theme(plot.title = element_text(size = 12, face = "bold",hjust = 0.5))

@@

# Graph histogram
# Create the histogram with mean line
cut_histogram_plot <- ggplot(cleaned_data, aes(x = cut)) +
  geom_bar(bins = 20, fill = "palevioletred", color = "black", alpha = 0.7)+
  labs(
    title = "Distribution of Variable: Cut",
    x = "Diamond Cut",
    y = "Count"
  ) +
  theme_minimal()+
  theme(plot.title = element_text(size = 12, face = "bold",hjust = 0.5))

violin_plot_cut <- ggplot(cleaned_data, aes(x = cut, y = price)) +
  geom_violin(trim = FALSE, fill = "lightblue", alpha = 0.7) + 
  geom_boxplot(width = 0.2, outlier.color = "salmon", outlier.shape = 8, alpha = 0.7) +
  labs(
    title = "Violin Plot of Price by Cut",
    x = "Diamond Cut",
    y = "Diamond Price (USD)"
  ) +
  theme_minimal()+
  theme(plot.title = element_text(size = 12, face = "bold",hjust = 0.5))

@@

@@

@@

@@

\begin{itemize}
    \item \( x_{1i} \): The carat size of the diamond (in carats).
    \item \( x_{2i} \): The color grade of the diamond (categorical).
    \item \( x_{3i} \): The cut grade of the diamond (categorical).
    \item \( x_{4i} \): The clarity grade of the diamond (categorical).
\end{itemize}

**Model Structure**:
1. **Response Distribution**:  
   \[
   y_i \mid \mu_i, \phi \sim \text{Gamma}(\mu_i, \phi),
   \]
   where \( \mu_i \) is the mean price and \( \phi \) is the dispersion parameter.

2. **Link Function**:  
   \begin{align}
   \log(\mu_i) &= \beta_0 + \beta_1 x_{1i} 
   + \sum_{j} \beta_{2j} \cdot \text{color}_{ij} \nonumber \\
   &\quad + \sum_{k} \beta_{3k} \cdot \text{cut}_{ik} 
   + \sum_{l} \beta_{4l} \cdot \text{clarity}_{il}.
   \end{align}
   - \( \beta_0 \): Intercept term.  
   - \( \beta_1 \): Effect of carat size.  
   - \( \beta_{2j}, \beta_{3k}, \beta_{4l} \): Effects of color, cut, and clarity, respectively.

3. **Mean Price**:  
   \begin{align}
   \mu_i &= \exp\left(\beta_0 + \beta_1 x_{1i} 
   + \sum_{j} \beta_{2j} \cdot \text{color}_{ij} \right. \nonumber \\
   &\quad \left.+ \sum_{k} \beta_{3k} \cdot \text{cut}_{ik} 
   + \sum_{l} \beta_{4l} \cdot \text{clarity}_{il}\right).
   \end{align}
